Reproducibility in Plant Pathology

### 2022-07-04 README.rmd
Correct preprint year
Reknit README and paper and supplementary materials

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (2021). _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_. agriRxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31220/agriRxiv.2021.00082>

@@

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the [Word document](analysis/paper/paper.docx) in a Docker session.

>>>>

> Sparks, A.H., Del Ponte, E.M., Alves, K. S., Foster, Z., Grünwald, N. J. (2022). _Openness and computational reproducibility in plant pathology: where do we stand and a way forward_. agriRxiv, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31220/agriRxiv.2021.00082>

@@

A script, `knit_paper.R`, is located in `analysis/paper/knit_paper.R` that will knit the [manuscript](analysis/paper/paper.docx) and the [supplementary materials](analysis/supplementary-materials.docx) in a Docker session.
